Binocular combination in the autonomic nervous system

### 2024-06-06 manuscript.Rmd
Added significance statement and started doing some formatting changes to the title page.

$^1$Department of Psychology, University of York, Heslington, York, United Kingdom.

$^2$School of Psychology and Vision Sciences, University of Leicester, Leicester, United Kingdom.

$^3$School of Philosophy, Psychology and Language Sciences, University of Edinburgh, Edinburgh, United Kingdom.

$^4$York Biomedical Research Institute, University of York, Heslington, York, United Kingdom.

@@

@@

```{r phaseplots, fig.cap="Pupil phase plots at the first and second harmonic frequencies for the luminance, melanopsin, L-M pathway and the S-(L+M) pathway conditions Panel (a) shows the pupil response at the first harmonic frequency during binocular stimulation. Panel (b) shows the pupil response at the second harmonic frequency during binocular stimulation. The five data points for each pathway correspond to the five contrast levels displayed. In panel (a) the luminance amplitudes have been scaled down by a factor of 10 to enable comparison with the other conditions.", fig.align="center", echo=FALSE}

>>>>

$^1$Department of Psychology, University of York, Heslington, York, YO10 5DD, United Kingdom.

$^2$School of Psychology and Vision Sciences, University of Leicester, Leicester, LE1 7RH, United Kingdom.

$^3$School of Philosophy, Psychology and Language Sciences, University of Edinburgh, Edinburgh, EH8 9AD, United Kingdom.

$^4$York Biomedical Research Institute, University of York, Heslington, York, YO10 5NG, United Kingdom.

@@

The diameter of the pupil depends on the level of ambient light and is controlled by distinct retinal photoreceptor classes (cones, rods and intrinsically photosensitive retinal ganglion cells). The computational processes behind binocular integration within the subcortical pathways controlling pupil dimension have been investigated and have been shown to occur independently of visual cortex. We investigated binocular combination within the different photoreceptor pathways using silent substitution. We found different patterns of binocular combination in each pathway and also differences in the phase of the pupil response. The results are consistent with a computational model of binocular signal combination, where the weight of interocular suppression differs across pathways, and demonstrate the algorithm governing binocular combination in the autonomic nervous system.

@@

```{r phaseplots, fig.cap="Pupil phase plots at the first and second harmonic frequencies for the luminance, melanopsin, L-M pathway and the S-(L+M) pathway conditions. Panel (a) shows the pupil response at the first harmonic frequency during binocular stimulation. Panel (b) shows the pupil response at the second harmonic frequency during binocular stimulation. The five data points for each pathway correspond to the five contrast levels displayed. In panel (a) the luminance amplitudes have been scaled down by a factor of 10 to enable comparison with the other conditions.", fig.align="center", echo=FALSE}

### 2024-06-06 manuscript.tex
Added significance statement and started doing some formatting changes to the title page.

\(^1\)Department of Psychology, University of York, Heslington, York, United Kingdom.

\(^2\)School of Psychology and Vision Sciences, University of Leicester, Leicester, United Kingdom.

\(^3\)School of Philosophy, Psychology and Language Sciences, University of Edinburgh, Edinburgh, United Kingdom.

\(^4\)York Biomedical Research Institute, University of York, Heslington, York, United Kingdom.

@@

@@

\caption{Pupil phase plots at the first and second harmonic frequencies for the luminance, melanopsin, L-M pathway and the S-(L+M) pathway conditions Panel (a) shows the pupil response at the first harmonic frequency during binocular stimulation. Panel (b) shows the pupil response at the second harmonic frequency during binocular stimulation. The five data points for each pathway correspond to the five contrast levels displayed. In panel (a) the luminance amplitudes have been scaled down by a factor of 10 to enable comparison with the other conditions.}\label{fig:phaseplots}
\end{figure}

>>>>

\(^1\)Department of Psychology, University of York, Heslington, York, YO10 5DD, United Kingdom.

\(^2\)School of Psychology and Vision Sciences, University of Leicester, Leicester, LE1 7RH, United Kingdom.

\(^3\)School of Philosophy, Psychology and Language Sciences, University of Edinburgh, Edinburgh, EH8 9AD, United Kingdom.

\(^4\)York Biomedical Research Institute, University of York, Heslington, York, YO10 5NG, United Kingdom.

@@

\hypertarget{significance-statement-120-words}{%
\section{Significance statement (120 words)}\label{significance-statement-120-words}}

The diameter of the pupil depends on the level of ambient light and is controlled by distinct retinal photoreceptor classes (cones, rods and intrinsically photosensitive retinal ganglion cells). The computational processes behind binocular integration within the subcortical pathways controlling pupil dimension have been investigated and have been shown to occur independently of visual cortex. We investigated binocular combination within the different photoreceptor pathways using silent substitution. We found different patterns of binocular combination in each pathway and also differences in the phase of the pupil response. The results are consistent with a computational model of binocular signal combination, where the weight of interocular suppression differs across pathways, and demonstrate the algorithm governing binocular combination in the autonomic nervous system.

@@

\caption{Pupil phase plots at the first and second harmonic frequencies for the luminance, melanopsin, L-M pathway and the S-(L+M) pathway conditions. Panel (a) shows the pupil response at the first harmonic frequency during binocular stimulation. Panel (b) shows the pupil response at the second harmonic frequency during binocular stimulation. The five data points for each pathway correspond to the five contrast levels displayed. In panel (a) the luminance amplitudes have been scaled down by a factor of 10 to enable comparison with the other conditions.}\label{fig:phaseplots}
\end{figure}
